Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks

### 2020-03-10 paper/eccv2020submission.tex
Adding some small parts to the paper

@@

Two of the models also take certain simulation parameters as inputs. In all cases the parameters are real values. In order for the network to be able to use them as part of the input, we transform these values in a constant single channel images with a value equal to the one of the parameter. This means that for each simulation parameter there is an extra channel in the for the generator network. Thus, depending on the model being trained, the network can take anywhere between 3 (velocity fields and object mask) and 6 (velocity and pressure fields, object mask and two parameter channels) channel input.

The output of the generator, however, is limited to either 2 or 3 channel image depending on whether the pressure field is used or not.

>>>>

Because the number of simulations in each set is different, we also generated different number of images per simulation based on the corresponding set. For the plain dataset, we rendered 1904 frames of the simulation (66 seconds of simulated physical time). For the inflow speed dataset --- overall 10050 frames coming from the 40 simulations (335 frames per simulation for 12 seconds of simulated physical time). For the viscosity-density model --- overall 104328 frames from 334 simulation (322 frames per simulation for 11 seconds of simulated physical time). Even though the simulation in the different datasets represent different time intervals, they are all long enough to develop the flow patterns that we are interested in.

@@

Two of the models also take certain simulation parameters as inputs. In all cases the parameters are real values. In order for the network to be able to use them as part of the input, we transform these values in a constant single channel images with a value equal to the one of the parameter. This means that for each simulation parameter there is an extra channel in the for the generator network. Thus, depending on the model being trained, the network can take anywhere between 3 (velocity fields and object mask) and 6 (velocity and pressure fields, object mask and two parameter channels) channel input. The output of the generator, however, can either be 2 or 3 channel image depending on whether the pressure field is used or not.

For the training procedure we follow the standard approach proposed by []. With each mini-batch we first optimize the discriminator and then the generator with the discussed objectives. We use Stochastic Gradient Descent [] with the Adam optimizer with a learning rate of $0.0002$ and momentum parameters $\beta_1=0.9$ and $\beta_2=0.999$.

The used batch size for the constant and inflow speed models was set to 3 and for the viscosity-density models to 4. Those are relatively small numbers for batch sizes but [] suggests that the UNet architecture benefits from small batches in image-to-image translation problems. Our experiments confirmed this.

Because of the differences in the amount of data available for training each model type, suitable epoch numbers were chosen for each of them. The constant models were trained for 45 epochs, the inflow speed models for 30 epochs and the viscosity-density models for 10 epochs.

All of the models were trained and evaluated on a single Nvidia GTX 980Ti GPU.\@
